EvoSuite at the SBST 2016 Tool Competition

### 2016-02-18 papers/sbst16/paper_sbst16.tex
Update paper

%We configured \EVOSUITE to use a dynamic timeout of maximum 10 minutes
%per class for the search, with an earlier stop if the fitness value
%did not increase for two minutes. The fitness function to drive the
%genetic algorithm was based on a combination of line coverage, branch
%coverage, and weak mutation testing~\cite{emse14_mutation}. We enabled
%the post-processing step of test minimization, but to reduce the time
%spent we included all assertions rather than filtering them with
%mutation analysis~\cite{10.1109/TSE.2011.93}. In practice, this may
%not result in the most readable or maintainable test cases, but
%neither of these two attributes is measured by the SBST contest
%metric.

@@

[]

@@

>>>>

\EVOSUITE can be configured to target different coverage criteria. The
fitness function to drive the genetic algorithm was based on a
combination of several criteria~\cite{rojas2015combining} (e.g., line
coverage, branch coverage, branch coverage by direct method
invocation, weak mutation testing, output coverage, exception
coverage). \EVOSUITE now by default uses an archive of
solutions~\cite{emse_archive}, which means that throughout the search,
whenever a new coverage goal is satisfied, the corresponding test is
stored in the archive, and this goal is no longer targeted by the
fitness function. We enabled the post-processing step of test
minimization, but to reduce the time spent we included all assertions
rather than filtering them with mutation
analysis~\cite{10.1109/TSE.2011.93}. The use of all assertions has
effects on readability and the chances of obtaining flaky
tests. However, as readability is not measured by the SBST contest
metric, and many of the improvements to \EVOSUITE since the last
competition target flaky tests we deemed this not a problem.

In contrast to previous instances of the competition, the test
generation tools this time received a time budget as input, and then
had to generate tests within that time. \EVOSUITE uses a combination
of different timeouts for its individual phases (e.g., initialization,
search, minimization, assertion generation, compilation check, removal
of flaky tests), which created the challenge of distributing the
overall budget onto these phases. We used a simple approach where 50\%
of the time was allocated to the search, whereas the other half of the
time was distributed equally to the remaining phases. If any of the
phases used more time than allocated, which can for example happen if
test executions take long or lead to timeouts, then phases for which
there is no time left are skipped. For example, if there is no time
left for minimization, then the raw test suite as generated by the
search is returned.

@@

Following recent experiments on
Defects4J~\cite{shamshiri2015automatically} that revealed general
issues in unit test generation, \EVOSUITE now includes assertions on
the source of exceptions, similar to commercial tools like Agitar
One~\cite{agitarone}. However, there were several instances in the
competition where these assertions lead to flaky tests. For example,
the following is an excerpt from a test for the Defects4J bug Lang-41,
generated by \EVOSUITE:

\begin{lstlisting}
@Test(timeout = 4000)
public void test19()  throws Throwable  {
 Class<Double> class0 = Double.class;
 String string0 = ClassUtils.getPackageName(class0);
 try { 
   ClassUtils.getClass(string0);
   fail("Expecting exception: ClassNotFoundException"); 
 } catch(ClassNotFoundException e) {
   assertThrownBy("java.net.URLClassLoader", e);
 }
}
\end{lstlisting}

While compiling and executing this test with JUnit works without
problems, the mutation analysis step of the competition used Ant to
run the tests; Ant uses a complex setup of classloaders that
eventually leads to the \texttt{assertThrownBy} in the above example
to fail, as the source of the exception is a different one.

@@

Many thanks to all the contributors to \EVOSUITE.
